True versus apparent shapes of astrophysical bow shocks

### 2016-01-29 papers/Paper1/sec-application.tex
Last edit to application section

 Combining equations (6),(9)-(11) and (19)-(23) from \citep{Canto:1996} and (\ref{eq:nprop}), we can solve numerically for $R(\theta)$, which gives us the shell's shape. Also we can
obtain a relation between $\theta$ and $\theta_1$

\begin{align}
\theta_1\cot\theta_1 = 1+ 2\beta I(\theta)\cot\theta - \frac{4}{5}\beta\left(1-\cos^{5/2}\theta\right)
\label{eq:th1th}
\end{align}

Where $I(\theta)\equiv \int^\theta_0 \cos^{1/2}\theta\sin^2\theta$

\begin{figure}
\includegraphics[width=\linewidth]{r-beta}
\caption{Bow shock shapes obtained with the \citep{Canto:1996} algebraic formalism using (\ref{eq:nprop}) to describe the proplyd wind density. The distance are normalized with $D$
to avoid dependency with this parameter.}
\end{figure}

@@

@@

Combining equation (23) from \citep{Canto:1996} and  (\ref{eq:th1th}) evaluated at $\theta=\frac{\pi}{2}$, we can obtain $R_{90}$

\begin{align}
R_{90} \simeq \frac{\left(2.4\beta\right)^{1/2}}{1-0.8\beta}
\label{eq:r90}
\end{align}

Expanding (\ref{eq:th1th}) until order 3th around $\theta=0$, we found for $\theta \ll 1$ that $\theta_1\simeq \beta^{1/2}\theta$.

>>>>

If we apply the \citep{Canto:1996} formalism for a photoevaporated flow with density given by (\ref{eq:nprop}), we find that the solutions for equations (8) - (11) of \citep{Canto:1996} are the following:

\begin{align}
\dot{M}_w &= \frac{\dot{M}_w^0}{3}\left(1-\cos^{3/2}\theta\right) \label{eq:dotprop} \\
\dot{\Pi}_z &= \frac{1}{5}v_w \dot{M}_w^0\left(1-\cos^{5/2}\theta\right)  \label{eq:pir}\\
\dot{\Pi}_r &= \frac{1}{2}v_w\dot{M}_w^0\left(\frac{4}{5}E\left(\frac{\theta}{2}|2\right) - \frac{1}{5}\sin 2\theta\cos^{1/2}\theta\right) \label{eq:piz}\\
\dot{J}_w = 0 \label{eq:jdot}
\end{align}  
The solution for (\ref{eq:piz}) includes an incomplete elliptic integral of the second kind. Combining equations  (\ref{eq:dotprop}) to (\ref{eq:jdot}) with equation (6) of \citep{Canto:1996}
numerically in python code, we can obtain the bow shock shape $R(\theta)$, as illustred in figure (\ref{fig:r-beta}).

% Combining equations (6),(9)-(11) and (19)-(23) from \citep{Canto:1996} and (\ref{eq:nprop}), we can solve numerically for $R(\theta)$, which gives us the shell's shape. Also we can
%obtain a relation between $\theta$ and $\theta_1$

%\begin{align}
%\theta_1\cot\theta_1 = 1+ 2\beta I(\theta)\cot\theta - \frac{4}{5}\beta\left(1-\cos^{5/2}\theta\right)
%\label{eq:th1th}
%\end{align}

%Where $I(\theta)\equiv \int^\theta_0 \cos^{1/2}\theta\sin^2\theta~d\theta$. The solution of this integral is an incomplete elliptical integral of the second kind:

%\begin{align}
%\int^\theta_0 \cos^{1/2}\theta\sin^2\theta~d\theta = \frac{4}{5}E\left(\frac{\theta}{2}|2\right) - \frac{1}{5}\sin 2\theta\cos^{1/2}\theta
%\end{align}

\begin{figure}
\includegraphics[width=\linewidth]{r-beta}
\caption{Bow shock shapes obtained with the \citep{Canto:1996} algebraic formalism using (\ref{eq:nprop}) to describe the proplyd wind density. The distance are normalized with $D$
to avoid dependency with this parameter.}
\label{fig:r-beta}
\end{figure}

@@

In order to find an analytic form of the characteristic radii $(R_0,R_c,R_{90})$, we may combine equations (\ref{eq:dotprop}) to (\ref{eq:jdot}) with (6) and (23) from \citep{Canto:1996}
and obtain the following relation:

\begin{align}
\theta_1\cot\theta_1 -1 =  \frac{8}{5}\beta E\left(\frac{\theta}{2}|2\right)\cot\theta - \frac{4}{5}\beta
\label{eq:th1th}
\end{align}

@@

We can obtain $R_{90}$ by the following process:
Evaluating equations  (\ref{eq:th1th}) and (23) from \citep{canto:1996} at $\theta=\frac{\pi}{2}$ we obtain the following:

\begin{align}
R_{90} &= D\tan\theta_{1,90} \\
\theta_{1,90}\cot\theta_{1,90} &= 1-\frac{4}{5}\beta \label{eq:th190}
\end{align}
Where $\theta_{1,90}\equiv \theta_º(\frac{\pi}{2})$. Combining both equations we have:

\begin{align}
R_{90} &= D\frac{\theta_{1,90}}{1-\frac{4}{5}\beta} 
\end{align}

Expanding (\ref{eq:th190}) until 3rd order and solving for $\theta_{1,90}$:
\begin{align}
\theta_{1,90} \simeq \left(\frac{2.4\beta}{1-0.8\beta}\right)^{1/2} \\
R_{90} \simeq \left(\frac{2.4\beta}{(1-0.8\beta)^3}\right)^{1/2}
\label{eq:r90}
\end{align}
%%%% Here we go in edition

Now, to obtaining $R_c$ we expand  (\ref{eq:th1th}) until order 2nd order for small $\theta$ values to find that for such values
$\theta_1 = \beta^{1/2}\theta$
